Dominance Regions for Affine Cluster Algebras

### 2022-06-30 affine_dominance.tex
Another ugly formula
Something much nicer

@@

>>>>

          \label{eq:negative g-vector mutations}
          (-1)^s\lambda'_k =
            \lambda_k+\sum_{0\le v_0<v_1<\cdots<v_q\le s}\sum\limits_{\substack{\ell\le \ell^{(v_0)}_1<\cdots<\ell^{(v_0)}_{m_{v_0}}\le n\\ 1\le \ell^{(v_1)}_1<\cdots<\ell^{(v_1)}_{m_{v_1}}\le n\\ \vdots\\ 1\le \ell^{(v_q)}_1<\cdots<\ell^{(v_q)}_{m_{v_q}}\le n}} \prod\limits_{p=0}^q \Big( b_{\ell^{(v_{p-1})}_{m_{v_{p-1}}}\ell^{(v_p)}_1} \prod\limits_{w=2}^{m_{v_p}} b_{\ell^{(v_p)}_{w-1} \ell^{(v_p)}_w} \Big)\lambda_{\ell^{(v_q)}_{m_{v_q}}} & \text{if $1\le k\le \ell-1$;}\\
            -\lambda_k-\sum_{0\le v_0<v_1<\cdots<v_q\le s}\sum\limits_{\substack{\ell\le \ell^{(v_0)}_1<\cdots<\ell^{(v_0)}_{m_{v_0}}\le n\\ 1\le \ell^{(v_1)}_1<\cdots<\ell^{(v_1)}_{m_{v_1}}\le n\\ \vdots\\ 1\le \ell^{(v_q)}_1<\cdots<\ell^{(v_q)}_{m_{v_q}}\le n}} \prod\limits_{p=0}^q \Big( b_{\ell^{(v_{p-1})}_{m_{v_{p-1}}}\ell^{(v_p)}_1} \prod\limits_{w=2}^{m_{v_p}} b_{\ell^{(v_p)}_{w-1} \ell^{(v_p)}_w} \Big)\lambda_{\ell^{(v_q)}_{m_{v_q}}} & \text{if $\ell\le k\le n$;}

@@

  Define an infinite quiver $\widehat{Q}$ with vertices $(k,s)\in [n]\times\ZZ_{\ge0}$ and the following arrows:
  \begin{itemize}
    \item an arrow $(\ell,s)\to (k,s)$ of weight $b_{k\ell}$ whenever $k<\ell$ and $s\ge0$;
    \item an arrow $(k,s+1)\to (\ell,s)$ of weight $-b_{k\ell}$ whenever $k<\ell$ and $s\ge0$;
    \item an arrow $(k,s+1)\to (k,s)$ of weight $-1$ whenever $s\ge0$.
  \end{itemize}
  Given a path $p$ in $\widehat{Q}$, write $\wt(p)$ for the product of the weights along the arrows in $p$.
  Let $i(p)$ and $t(p)$ denote the initial and terminal vertex along the path $p$.
  Write $\hgt(p)$ for the largest $s$ appearing as the second component of a vertex along the path $p$.
  Then for $r<0$ with $r=ns+\ell$ for $1\le\ell\le n$, we have
  \[\lambda'_k=\begin{cases}\sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s-1, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $1\le k\le\ell-1$;}\\ \sum\limits_{\substack{p\subset\widehat{Q}\\ \hgt(p)=-s, t(p)=(k,0)}}\wt(p)\lambda_{i(p)} & \text{if $\ell\le k\le n$;} \end{cases}\]
